---
title: "Home Work Assignment 4"
author: "Pradeep Sahoo"
date: "7/1/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE)
```
My Github repository for my assignments can be found at this URL: [My Github ](https://github.com/Pradeep-Sahoo/R-Assignments/tree/master/R_Project1)

```{r load packages,warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library(nycflights13)
```

```{r}
not_cancelled <- flights %>%
  filter(!is.na(dep_delay), !is.na(arr_delay))
```

2.Come up with another approach that will give you the same output as

```{r}
not_cancelled %>% 
  count(dest)

```

count function counts  the data set by a the specified variable. The same result can be achieved if we group by the data set by the same variable. Then using length() function counts the observation in each group

```{r}
not_cancelled %>% 
  group_by(dest) %>%
  summarise(n = length(dest))
```

```{r}
not_cancelled %>% 
  count(tailnum, wt = distance)
```

```{r}
not_cancelled %>% 
  group_by(tailnum) %>%
  summarise(n = sum(distance))
```

3. Our definition of cancelled flights (
{ Snip }
is.na(dep_delay) | is.na(arr_delay) ) is slightly suboptimal. Why? Which is the most important column?

I think arr_delay is important. Because if the flight may go land in a different airport other than the Destination Airport. In that case the arr_delay would be NULL. So to know the about the Cancelled Flight both Dep_delay and Arr_delay has to be NULL

4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?

Need tto check with robert

```{r}
#canceled_delayed <- 
 # flights%>%
#group_by(flights, year, month, day)

```


```{r}
  flights%>%
  group_by(carrier)%>%
  summarise(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(desc(arr_delay))
```
```{r}
flights%>%
  count(carrier)%>%
  arrange((carrier))
```
```{r}
as_tibble(flights)
```

```{r}
mtcars
```

```{r}
class(mtcars)

```

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$abc
df$xyz
df[, "xyz"]
df[, c("abc", "xyz")]
```
If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

```{r}
my_data<-read.delim("/Users/pradeepsahoo/Downloads/baby_names.txt")
glimpse(my_data)
write.csv(my_data, file = "/Users/pradeepsahoo/Downloads/baby_names.csv")
my_csv <- read_csv("/Users/pradeepsahoo/Downloads/baby_names.csv")
glimpse(my_csv)
```

