---
title: "Home Work Assignment 3"
author: "Pradeep Sahoo"
date: "6/21/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: [My Github ](https://github.com/Pradeep-Sahoo/R-Assignments/tree/master/R_Project1)

###Exercises
##Section 3.8.1: all exercises


```{r load packages,warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library(nycflights13)
```


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

By selecting Hwy and Cty we are plotting continous variable for X and Y. To get some information out of it we should have Positions. That will help to segregate these continous variable. 

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point(position = "jitter")
```

**giom_jitter function adds some amount of random variation to the location of each point. This is way to handling overplotting caused by discretness in datasets. 

This has 2 parameters, width and height. Width gives a x axis variation, Height gives a Y axis variation. 




```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_jitter(width = 0, height = 10)
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_jitter(width = 10, height = 0)
```


```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_jitter(width = 10, height = 10)
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_count(position = 'jitter')
```

```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) +
  geom_boxplot()
```


```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy, color = drv)) +
  geom_boxplot(position = 'identity')
```


##Section 3.9.1: #2 and #4 only

#1
```{r}
ggplot(mpg, aes(x = class, fill = drv)) +
  geom_bar()
```

```{r}
ggplot(mpg, aes(x = class, fill = drv)) +
  geom_bar() + coord_polar()
```

#4
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

coord_fixed() - This function fixes the line exactly to the points where cty mileage and hwy mileage matches. It draws the line connecting those points. 
This gives a perspective to the occurances of the Data. 

geom_abline() - This function draws a reference line. This reference line is used to give inference about the data occurances. 

##Section 4.4: #1 and #2 only

#1
Spelling Mistake.

```{r}
my_variable <- 10
my_variable
```
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
```


##Section 5.2.4: #1, #3 and #4 only. You will need to install the nycflights13 package and use the flights data.

#1
Had an arrival delay of two or more hours
```{r}
glimpse(flights)
filter(flights, arr_delay > 120)
```

Flew to Houston (IAH or HOU)
```{r}
filter(flights, dest %in% c("HOU","IAH"))
```

Were operated by United, American, or Delta
```{r}
filter(flights, carrier %in% c("UA","AA","DL"))
```

Departed in summer (July, August, and September)
```{r}
filter(flights, month >= 7 ,  month <=9)
```

Arrived more than two hours late, but didn’t leave late

```{r}
filter(flights, arr_delay > 120 , dep_delay <= 0)
```

Were delayed by at least an hour, but made up over 30 minutes in flight
```{r}
filter(flights,  dep_delay >=60, (dep_delay - arr_delay) > 30)
```

Departed between midnight and 6am (inclusive). Note that in dep_time, midnight is 2400, not 0.

```{r}
filter(flights,   dep_time <=600 )
```


#3
How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
filter(flights,   is.na(dep_time)  )
```

These flights never took off, so cancelled. 
#4
Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

##Need to check with Robert.


##Section 5.4.1: #1 and #3 only

#1 Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
```

#2 What happens if you include the name of a variable multiple times in a select() call?

```{r}
select(flights,dep_time,dep_time,arr_time,arr_delay)
```

R Markdown will remove the duplicate variable name and gives only variables. 

#3 What does the one_of() function do? Why might it be helpful in conjunction with this vector?

#4 Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("TIME"))
```

