---
title: "Pradeep Sahoo Home Work 1"
author: "Sahoo Pradeep"
date: "6/12/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: [My Github ](https://github.com/Pradeep-Sahoo/R-Assignments/tree/master/R_Project1)


```{r load packages,warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
```

```{r}
data(WorldCities)
```

##**QUESTION 1: How many observations and variables are there in this data set? What are some of the variable names? Type up your answer in your document using complete sentences.**

```{r}
glimpse(WorldCities)
```
```{r select 200 rows}
WorldCities <- head(WorldCities, 200) # 200 rows
```

```{r selecting countries}
country_col <- WorldCities$country
unique(country_col)
```

##**QUESTION 2: There is a column called region in the data set. Can you extract this and show only the unique values?**

```{r}
country_col <- select(WorldCities, country)
country_col <- WorldCities %>% select(country)
```

```{r}
WorldCities %>% select(region) %>% head(5)
```

##**QUESTION 3: Can you extract and show the unique entries from the country column in WorldCities using one line of code and two %>% operators?**

```{r}
WorldCities %>% select(country) %>% unique() 
```

###Visualize it

```{r}
WorldCities %>% ggplot(aes(x = population)) + 
  geom_histogram()
```

```{r}
WorldCities %>% ggplot(aes(x = population)) + 
  geom_histogram() + 
  xlab('City Population')
```

##**QUESTION 4: Make one more histogram of the population and add a new x-label, a new y-label, a new title (use ggtitle('my title')), and change the theme of the plot using theme_bw().**

```{r}
WorldCities %>% ggplot(aes(x = population)) + 
  geom_histogram() + 
  xlab('City Population') + 
  ylab('Count') +
  ggtitle('World Population') +
  theme_bw()
```





