---
title: "Pradeep Sahoo Midterm"
author: "Pradeep Sahoo"
date: "7/5/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: [My Github ](https://github.com/Pradeep-Sahoo/R-Assignments/tree/master/R_Project1)


```{r load packages,warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library(tibble)
```
#The tidyverse packages
1. Can you name which package is associated with each task below?
  a. Plotting - ggplot2
  b. Data munging/wrangling - dplyr
  c. Reshaping (speading and gathering) data - tidyr
  d. Importing/exporting data - readr
2. Now can you name two functions that you’ve used from each package that you listed above for these tasks?
 a. Plotting - ggplot(), geom_boxplot()
 b. Data munging/wrangling - summarize(), filter()
 c. Reshaping data - gather(), spread(), separate(), unite()
 d. Importing/exporting data - read_csv(), read_tsv(), read_delim()
 
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
My_data.name___is.too00ooLong
my_string <- c('has','an','error','in','it')
my_string
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```
my_vector is converted to string. 
```{r}
file_path = ('/Users/pradeepsahoo/Downloads/rail_trail.txt')
text_data <- read.delim(file_path,header = TRUE, sep = "|")
glimpse(text_data)
write.csv(text_data,file = '/Users/pradeepsahoo/R-Assignments/R_Project1/rail_trail.csv')
csv_data <- read.csv( '/Users/pradeepsahoo/R-Assignments/R_Project1/rail_trail.csv')
glimpse(csv_data)
```

```{r}

```

